Variational Monte Carlo on bosonic systems

### 2018-03-23 project_1/article/article.tex
Initial comments on initial results.

@@

    \subsection{Non-Interacting Systems}
    Initially we are interested in seeing how our implementation performs and to what extent it functions properly.
    the logical thing to do would be to look at a non-interacting system with a simple Gaussian wavefunction and
    harmonic oscillator potential. Such a system has a simple closed-form analytic solution\footnote{A fact that every
    undergraduate physics student should be well aware of.}, which is further simplified by the "god-given" analytic
    units (\autoref{eq:closed_form_natural_units_local_energy}). This expression is minimised for
    $\alpha = \frac{1}{2}\omega$. We also set $\omega = 1$ and get an expression for the
    expected minimum local energy,
    \begin{equation}
        E_L(\vb{r}) = \frac{dN}{2},
    \end{equation}
    which will be used as the benchmark we are ultimately aiming for.

@@

>>>>

		\subsection{Gradient Descent}

		The method of

@@

    \subsection{Non-Interacting Systems}
    Initially we are interested in seeing how our implementation performs and to what extent it functions properly.
    the logical thing to do would be to look at a non-interacting system with a simple Gaussian wavefunction and
    harmonic oscillator potential. Such a system has a simple closed-form analytic solution\footnote{A fact that every
    undergraduate physics student should be well aware of after finishing their first course in quantum physics}, 
    which is further simplified by the "god-given" analytic
    units (\autoref{eq:closed_form_natural_units_local_energy}). This expression is minimised for
    $\alpha = \frac{1}{2}\omega$. We also set $\omega = 1$ and get an expression for the
    expected minimum local energy,
    \begin{equation}
        E_L(\vb{r}) = \frac{dN}{2},
    \end{equation}
    which will be used as the benchmark we are ultimately aiming for.

@@

	For the first

	\autoref{tab:1D1N_analytic} shows the expected local energy $\expval{E_L}$, standard deviations 
	$\sigma$, $\sigma_b$, the share of accepted Monte Carlo reorientations $A$ and cpu time for 
	the analytic computation at different values for the variational parameter $\alpha$.
	\autoref{tab:1D1N_numeric} shows the same numbers but for the numeric scheme. The first column of
	standard deviations $\sigma$ are the "naïve" standard deviations, while $\sigma_b$ marks the
	standard deviations computed with the blocking method. One can clearly see, in both the analytic and numeric
	case, that the former standard deviations are lower than the latter, meaning that autocorrelated data
	can lead to a lower perceived uncertainty than what is reality. The blocking method takes this fact into account 
	and for this reason, all other standard deviations will be computed with the blocking method from here on.
